---
title: "R Markdown Example"
author: "NDJ"
date: "6/12/2019"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

This is a package that allows me to round results neatly.

```{r load_packages, include=FALSE}
library(broman)
```

For example:

```{r rounding_example, include=TRUE, echo=TRUE}
x <- rnorm(100)
y <- 2*x + rnorm(100)
myround(cor(x, y), 2)
```

This is a simple example of a Markdown document.

Use a blank link between paragraphs.
You can use a bit of **bold** or _italics_. Use backticks to indicate
`code` that will be rendered in monospace.

Here's a list:

- an item in the list
- another item
- yet another item

It'll figure out numbered lists, too:

1. First item
2. Second item

And it's easy to create links, like to
the [Markdown](https://daringfireball.net/projects/markdown/)
page.

You can include blocks of code using three backticks:

```{r simulate_data}
x <- rnorm(100)
y <- 2*x + rnorm(100)
plot(x, y)
```

The initial line in a code chunk may include various options. For example, echo=FALSE indicates that the code will not be shown in the final document (though any results/output would still be displayed).

```{r chunk_name, echo=FALSE}
x <- rnorm(100)
y <- 2*x + rnorm(100)
cor(x, y)
```

You use results='hide' to hide the results/output (but here the code would still be displayed).

```{r chunk_name2, results='hide'}
x <- rnorm(100)
y <- 2*x + rnorm(100)
cor(x, y)
```

You use include=FALSE to have the chunk evaluated, but neither the code nor its output displayed.

```{r chunk_name3, include=FALSE}
x <- rnorm(100)
y <- 2*x + rnorm(100)
cor(x, y)
```

If I’m writing a report for a collaborator, I’ll often use include=FALSE to suppress all of the code and largely just include figures.

For figures, you’ll want to use options like fig.width and fig.height. For example:

```{r scatterplot, fig.width=8, fig.height=6}
plot(x,y)
```

That's the end of my markdown test.


